\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-06-19 background.tex
Added the background section

>>>>

\subsection{Brief introduction to SystemJ syntax, semantics and model of
  computation}
\label{sec:brief-intr-syst}

\begin{table}[tb]
\centering
\caption{SystemJ kernel statements and their meaning}
\begin{minipage}{8cm}
  \begin{small}
   \begin{tabular}{|c|p{80pt}|}
     \hline                                                                                     
     \textbf{Kernel Statements} & \textbf{Meaning}\\                                            
     \hline                                                                                     
     \hline                                                                                     
     [\textbf{\texttt{input}}] [\textbf{\texttt{output}}]
     [\textbf{\texttt{type}}] \textbf{\texttt{signal}} S & declare signal S\\                                      
     \hline                                                                                     
     \textbf{\texttt{emit}} S [(value)] & broadcast signal S\\                                                    
     \hline                                                                                     
     \textbf{\texttt{present}} (S) \{p\} else \{q\}& do p if S is present, else do q\\                            
     \hline                                                                                     
     \textbf{\texttt{abort}} (S) \{p\} & preempt program p if S is present\\                                      
     \hline                                                                                     
     \textbf{\texttt{suspend}} (S)\{p\} & suspend p if S is present\\                                             
     \hline                                                                                     
     \textbf{\texttt{trap}} (T)\{p\ldots \textbf{\texttt{exit}} T\ldots\} & preempt p if exit is executed\\                         
     \hline                                                                                     
     p\textbf{\texttt{$||$}}q & run p and q in lock-step\\                                                        
     \hline                                                                                     
     p$><$q & run p and q asynchronously\\                                                      
     \hline                                                                                     
     \textbf{\texttt{send}} C([value]) & send a value through C, blocking
     send\\                                                 
     \hline                                                                                     
     \textbf{\texttt{receive}} C() & receive a value through C, blocking
     receive\\
     \hline                                                                                     
     \textbf{\texttt{pause}} & finish a tick and communicate
     with environment\\
     \hline                                                                                     
   \end{tabular}
  \end{small}
   % \footnotetext[1]{\scriptsize Uppercase}
 \end{minipage}
 \label{tab:1}
\end{table}

Table~\ref{tab:1} presents the SystemJ kernel statements used to program
the control flow. The data-flow is programmed in Java. A number of
derived statements also exist (e.g., \texttt{sustain}, \texttt{await},
etc) that make programming reactive systems easier. The \textit{Model of
  Computation} (MoC) of a simple SystemJ is shown in Figure~\ref{fig:2}.

\begin{figure*}[bth]
\centering
\begin{SubFloat}{\label{fig:2a}Simple SystemJ program}%...verbatim subfigure
\begin{minipage}[b]{0.3\linewidth}% a minipage to control the width...
\begin{verbatim}
while(true){
 abort(A){
  while(true)
   pause;
  emit O;
  // do java computation
}
\end{verbatim}%
\end{minipage}%
\end{SubFloat}
\hspace{1.5cm}%
\begin{SubFloat}[Black box]{\label{fig:2b}Ticks in SystemJ}%
\includegraphics[scale=0.5]{moc}
\end{SubFloat}%
\caption{Simple SystemJ example and corresponding MoC}
\label{fig:2}
\end{figure*}

SystemJ consists of entities called clock-domains (CD)s, each running at
their individual pace. Each CD adheres to the \textit{perfect synchrony}
hypothesis, i.e., all statements execute instantaneously in zero
time. Only the \texttt{pause} statement consumes time, just like in
Esterel~\cite{gber931}. Consider the SystemJ program in
Figure~\ref{fig:2a}, it is waiting for an input signal producing logical
ticks (see Figure~\ref{fig:2b}). Once \texttt{A} is received at tick 4,
output \texttt{O} is emitted to the environment instantaneously.

\subsection{Mapping logical time to physical time}
\label{sec:mapping-logical-time}

The perfect synchrony hypothesis is ideal for programming the
synchronous sub-set of SystemJ. But, the real-world is not that
forgiving, execution of every \textit{micro-step} in the logical zero
time, requires $\delta$ physical time. Time for a complete reaction to
one or more input signal can thus be summarized as $\Delta = \Sigma
(\delta)$. We call $\Delta$ the reaction time. Obviously depending upon
the amount of computation required, $\Delta$ can vary, hence, in order
to satisfy the implicit restriction posed by the synchrony hypothesis --
no input event can be missed, one needs to calculate the \textit{Worst
  Case Reaction Time} (WCRT) and the resultant WCRT needs to be smaller
than the speed of the fastest input event, else the synchrony hypothesis
is violated. A substantial amount of research for calculating the WCRT
of synchronous programs~\cite{proop10,boldt07,wilhelm08} exists. We
refer the reader to any of these research articles, since WCRT analysis
is not the focus of this paper. The opposite of the WCRT is the
\textit{Best Case Reaction Time} (BCRT), we denote the WCRT and BCRT in
Figure~\ref{fig:2b} using \texttt{W} and \texttt{B}, respectively.

We now present two lemmas with proof sketch (due to lack of space) that
we require for the rest of the paper.

\begin{lemma}
  WCRT and BCRT analysis are invariant to values of conditional
  expressions.
\end{lemma}

\begin{proof}
  The physical time ($\delta$) taken by a conditional expression is at
  best affected by the type rather than the value of the
  conditional. Example, comparing the value of 2 floats might take
  longer than comparing the value of 2 integer types on some given
  platform. But, the time taken by the comparison instruction is
  invariant to the value itself.
\end{proof}

\begin{lemma}
  WCRT and BCRT analysis are invariant to channel communication.
\end{lemma}
\begin{proof}
  LATER ....
\end{proof}

### 2013-06-19 introduction.tex
Added the background section

Reactive languages~\cite{gber05,amal10} are a class of programming
languages used for designing and implementing \textit{reactive} systems,
which continuously respond to input from their environment. These
languages have been successfully used in programming a plethora of
systems such as fly by wire in Airbus~\cite{eairbus}, security
surveillance systems~\cite{amal121}, etc. Usually the working
environment of these reactive systems is also real-time. Yet, these
languages do not support describing real-time as first class language
constructs. For example, one cannot describe a simple real-time delay
\texttt{delay 0.2 ms} in these languages. These languages are based on
formal semantics, essential for the formal verification of functional
correctness of the developed programs, but leave non-functional
properties such as timing behavior as an implementation
detail~\cite{ringler00,boldt07}.

These languages only support discrete \textit{logical} clock rather than
a continuous clock. The period of the discrete logical clock (also
referred to as a \textit{logical tick}) is determined by the
responsiveness of the program and as opposed to a discrete
\textit{physical} clock is elastic. Although this timing model has
worked well for these languages in designing discrete systems there is
obviously a need to introduce continuous time since often implementation
models are in the continuous time
domain~\cite{DBLP:journals/pieee/SifakisTY03}.

@@

\begin{enumerate}
\item The real-time is modeled in the $\mathbb{Q}^{>0}$ domain of
  numbers, i.e., non-negative rational numbers.
\item We consider the property of \textit{non maximal-parallelism},
  i.e., we consider scheduling on constrained resources to be an
  integral part of the solution. To our knowledge we are the very first
  to do so.
\item Our solution does not change the functional or timing semantics of
  GALS and its subset synchronous programs, in fact, our solution does
  not require one to change the compiler at all.
\item Our solution gives complete control of under and over
  approximation of real-time to the system designer.
\end{enumerate}

>>>>

Reactive languages~\cite{gber05,amal10} are a class of programming
languages used for designing and implementing \textit{reactive} systems,
which continuously respond to input from their environment. These
languages have been successfully used in programming a plethora of
systems such as fly by wire in Airbus~\cite{eairbus}, security
surveillance systems~\cite{amal121}, etc. Usually the working
environment of these reactive systems is also real-time. Yet, these
languages do not support describing real-time as first class language
constructs. For example, one cannot describe a simple real-time delay
\texttt{delay 0.2 ms} in these languages. These languages are based on
formal semantics, essential for the verification of functional
correctness properties of the developed programs, but leave
non-functional properties such as timing behavior as an implementation
detail~\cite{ringler00,boldt07}. Arguably rightly so, because physical
time cannot be incorporated without information about the underlying
execution platform. But, one can still reason in terms of
\textit{logical} time. These languages support discrete \textit{logical}
clock rather than a continuous clock. The period of the discrete logical
clock (also referred to as a \textit{logical tick}) is determined by the
responsiveness of the program to the input signals and as opposed to a
discrete \textit{physical} clock is elastic. Although this timing model
has worked well for these languages in designing discrete systems there
is obviously a need to introduce continuous time since often
implementation models are in the continuous time
domain~\cite{DBLP:journals/pieee/SifakisTY03}.

@@

\begin{enumerate}
\item The real-time is modeled in the $\mathbb{Q}^{>0}$ domain of
  numbers, i.e., non-negative rational numbers.
\item We consider the property of \textit{non maximal-parallelism},
  i.e., we consider scheduling on constrained resources to be an
  integral part of the solution. To our knowledge we are the very first
  to do so.
\item Our solution does not change the functional or timing semantics of
  GALS and its subset synchronous programs, in fact, our solution does
  not require one to change the compiler at all.
\item Our solution gives complete control of under and over
  approximation of real-time to the system designer.
\item We are the first to allow specification of both deterministic and
  non-deterministic real-time.
\end{enumerate}
